%-------------------------
% Resume in Latex
% Author : Ian Dunn
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

% Clean underlines
\usepackage[normalem]{ulem}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\bfseries\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Change bullet points to use full width of page
\setlist[itemize]{leftmargin=*}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{\small#3} & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Ian Dunn} \\ \vspace{1pt}
    \textbf{\large Software Engineer} \\ \vspace{1pt}
    \small (585) 520-2110 $|$ 
    \href{mailto:iantdunn@gmail.com}{\uline{iantdunn@gmail.com}} $|$ 
    \href{https://iantdunn.com}{\uline{iantdunn.com}}
\end{center}

%-----------EXPERIENCE-----------

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Mindex}{Oct 2024 -- Present}
        {Associate Software Engineer}{Remote}
        \resumeItemListStart
            \resumeItem{Drove a \$4M increase in annual revenue with an enterprise microservice to automatically assign price tiers.}
            \resumeItem{Created a CSV ingestion pipeline from AWS S3 into MongoDB to process 5,500 records per minute.}
            \resumeItem{Implemented a Kafka consumer to propagate near real-time updates to downstream billing systems.}
            \resumeItem{Presented production changes to project stakeholders and documented handoff for client teams.}
        \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Aperture Solutions, LLC}{Mar 2025 -- Present}
      {Freelance Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Delivered end-to-end websites for small businesses, including a new client site with 130 monthly visitors.}
        \resumeItem{Evaluated Software as a Medical Device systems for regulatory compliance during pharmaceutical quality audits.}
        \resumeItem{Designed a custom CMS storefront using React, Spring Boot, and Postgres to provide control of product listings.}
      \resumeItemListEnd

      \resumeSubheading
      {RIT Laboratory of Software Design and Productivity}{Mar 2023 -- Aug 2023}
      {Software Security Team Lead}{Rochester, NY}
      \resumeItemListStart
        \resumeItem{Developed a REST API suite using Spring Boot and JSON/XML manipulation to create and analyze SBOMs.}
        \resumeItem{Led team planning meetings and presented burndown charts to leadership for each sprint.}
        \resumeItem{Deployed a scalable back-end platform and a custom open-source analysis utility using Docker Compose.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{MarketSNIPR} $|$ \emph{PyTorch, NumPy, Pandas}}{Aug 2024 -- Present}
            \resumeItemListStart
                \resumeItem{Developing a reinforcement learning trading agent that learns strategies using profit/loss reward functions.}
                \resumeItem{Researching TD3 learning to model stock price movements using technical indicators and sentiment analysis.}
                \resumeItem{Focusing on policy learning and simulation, with planned expansion to brokerage API integration.}
            \resumeItemListEnd
    
        \resumeProjectHeading
            {\textbf{\href{https://outthebasement.com}{\uline{outthebasement.com}}} $|$ \emph{React, Spring Boot, PostgreSQL, Docker}}{May 2025}
            \resumeItemListStart
                \resumeItem{Built a full-stack inventory management system using React, Spring Boot, and PostgreSQL.}
                \resumeItem{Designed REST APIs for CRUD operations, server-side image storage, and token-based authentication.}
                \resumeItem{Automated deployment to a DigitalOcean Droplet using Docker Hub and GitHub Actions CI/CD pipelines.}
            \resumeItemListEnd

        \resumeProjectHeading
            {\textbf{\href{https://github.com/Neurotechnology-Exploration-Team/DataCollector}{\uline{EEG Data Collector}}} $|$ \emph{Python, Tkinter}}{Dec 2023 -- May 2024}
            \resumeItemListStart
                \resumeItem{Created a Tkinter GUI application to capture brain activity in response to audiovisual stimuli.}
                \resumeItem{Documented the project's usage and scalability for adaptation by other research teams.}
            \resumeItemListEnd
          
    \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------

\section{Leadership}
  \resumeSubHeadingListStart
  
      \resumeSubheading
      {RIT Neurotechnology Exploration Team}{Dec 2023 -- May 2024}
      {Wheelchair Project Co-Investigator}{Rochester, NY}
      \resumeItemListStart
        \resumeItem{Pioneered a brain-motor interface project to enable people with motor dystrophy to operate a motorized wheelchair.}
        \resumeItem{Conducted an IRB-approved human subject research study to collect model training data.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd



%-----------EDUCATION-----------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rochester Institute of Technology}{Rochester, NY}
      {Bachelor of Science in Computer Science}{Aug 2021 -- May 2024}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------

\section{Technical Skills}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C\#, JavaScript/HTML/CSS, SQL (Oracle, PostgreSQL), MongoDB, C, PHP, Bash} \\
     \textbf{Frameworks}{: React, Node.js, Django, Flask, Express, Angular, Bootstrap, JUnit, Kafka, Nginx} \\
     \textbf{Developer Tools}{: Git, Docker, Jenkins, Jira, Confluence, OpenShift, JetBrains Suite, BitBucket, Ant} \\
     \textbf{Libraries}{: NumPy, Pandas, SciKit-Learn, OpenAI Gym, Avro}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
